Denotational Semantics of Gradual Typing using Synthetic Guarded Domain Theory

### 2024-10-25 paper-new/concrete-relational-model.tex
clarify the use of clocks in the relational adequacy section

To that end, we define a version of our denotation of term precision
that relates terms of type $\li^{gl} \mathbb{N}$. More concretely, consider the
predomain $\mathbb{N}$ with ordering and bisimilarity both the equality
relation. We define a global version of the lock-step error ordering and the
weak bisimilarity relation on elements of $\li^{gl} \mathbb{N}$; the former is
defined by
%
\( x \ltls^{gl} y := \forall k. x[k] \ltls y[k], \)
%
and the latter is defined by
%
\( x \bisim^{gl} y := \forall k. x[k] \bisim y[k]. \)
%

>>>>

To that end, we define, using clock quantification, a version of our denotation of term precision
that relates terms of type $\li^{gl} \mathbb{N}$. More concretely, consider the
predomain $\mathbb{N}$ with ordering and bisimilarity both the equality
relation. We define a global version of the lock-step error ordering and the
weak bisimilarity relation on elements of $\li^{gl} \mathbb{N}$; the former is
defined by
%
\( x \ltls^{gl} y := \forall k. x[k] \ltls y[k], \)
%
and the latter is defined by
%
\( x \bisim^{gl} y := \forall k. x[k] \bisim y[k]. \)
%
In these two definitions, we apply the clock $k$ to the elements $x$ and $y$ of
type $\li^{gl} \mathbb{N} := \forall (k : \Clock). \li^k \mathbb{N}$.
